Unshuffling Permutations

### 2015-09-27 submission.tex
Fig 6

        \foreach \x/\y in {12/5,13/4,14/3,15/2,16/1,17/0} {
            \draw [fill=black] (\x,\y) circle (0.1);
        }
        % labels
        \node [label] (x) at (2,4.5) {$x$};
        \node [label] (a) at (8,14.5) {$a$};
        \node [label] (xp) at (14,-1.5) {$x'$};
        \node [label] (ap) at (16,-1.5) {$a'$};
        \node (nu1) at (2.5,2.5) {$\nu_2$};
        \node (nu2) at (8.5,12.5) {$\nu_3$};
        \node (nu1') at (14.5,-3.5) {$\nu'_2$};
        % crossings edges
        \draw [line width=1pt]
        (2,9) .. controls +(0,25) and +(0,30) .. (14,3);
        \draw [line width=1pt]
        (8,18) .. controls +(0,15) and +(0,20) .. (16,1);
      \end{tikzpicture}
    \caption{\label{fig:subfig:no (nu_3, nu'_2)-edge}%
      Claim~\ref{claim:no (nu_3, nu'_2)-edge}:
      Assuming a $(\nu_3, \nu'_2)$-edge $(a, b)$ in $\mathcal{M}$.
    }
  \end{figure}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_3, nu'_2)-edge}]
    Suppose, aiming at a contradiction, that there exists
    $(\nu_3, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_2, nu'_2)-edge}, there
    exists at least one $(\nu_2, \nu'_2)$-edge $(x, x')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free (Lemma~\ref{lemma:matching}),
    we have $x' < a'$.
    Therefore,
    we have $\mu(x) < \mu(a)$ (since $\nu_2$ is below $\nu_3$) and
    $\mu(x') > \mu(a')$ (since $\nu'_2$ is decreasing),
    which contradicts our hypothesis about $\mathcal{M}$.
    See Fig.~\ref{fig:subfig:no (nu_3, nu'_2)-edge}.
    \qed
  \end{proof}

>>>>

        \foreach \x/\y in {12/5,13/4,14/3,15/2,16/1,17/0} {
            \draw [fill=black] (\x,\y) circle (0.1);
        }
        % labels
        \node [label] (x) at (2,4.5) {$b$};
        \node [label] (a) at (8,14.5) {$a$};
        \node [label] (xp) at (14,-1.5) {$b'$};
        \node [label] (ap) at (16,-1.5) {$a'$};
        \node (nu1) at (2.5,3.5) {$\nu_2$};
        \node (nu2) at (8.5,13.5) {$\nu_3$};
        \node (nu1') at (14.5,-2.5) {$\nu'_2$};
        % crossings edges
        \draw [line width=1pt]
        (2,9) .. controls +(0,25) and +(0,30) .. (14,3);
        \draw [line width=1pt]
        (8,18) .. controls +(0,15) and +(0,20) .. (16,1);
      \end{tikzpicture}
    \caption{\label{fig:subfig:no (nu_3, nu'_2)-edge}%
      Claim~\ref{claim:no (nu_3, nu'_2)-edge}:
      Assuming a $(\nu_3, \nu'_2)$-edge $(a, b)$ in $\mathcal{M}$.
    }
  \end{figure}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_3, nu'_2)-edge}]
    Suppose, aiming at a contradiction, that there exists
    $(\nu_3, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_2, nu'_2)-edge}, there
    exists at least one $(\nu_2, \nu'_2)$-edge $(b, b')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free (Lemma~\ref{lemma:matching}),
    we have $b' < a'$.
    Therefore,
    we have $\mu(b) < \mu(a)$ (since $\nu_2$ is below $\nu_3$) and
    $\mu(b') > \mu(a')$ (since $\nu'_2$ is decreasing),
    which contradicts our hypothesis about $\mathcal{M}$.
    See Fig.~\ref{fig:subfig:no (nu_3, nu'_2)-edge}.
    \qed
  \end{proof}
